Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-11 mtjournal.tex
removed call to ulem package -- strikeout not needed
overview paragraph at end of intro roughed in.

% TO DO: package provides \sout{} strikeout macro -- remove this
% before submission
\usepackage{ulem}

@@

% override ulem 's default change of \emph{} -- remove before ship
\normalem
\section{Introduction}
\label{sec:intro}

@@

TO DO: OVERVIEW OF THE REST OF THE PAPER

@@

\section{Experimental paradigm}
\label{sec:paradigm}
In this section, we outline the details of the implementation and
experimental variables explored in the experiments presented here.

>>>>

@@

\section{Introduction}
\label{sec:intro}

@@

In the following section (section~\ref{sec:approach}), we outline our
approach to including syntactic information in MT evaluation, by
describing a family of metrics. In section~\ref{sec:paradigm}, we
describe the implementation details and make explicit which dimensions
of this family of metrics we explore in this paper.
Section~\ref{sec:faexpts} examines the correlation of several members
of this family with human judgments of fluency and adequacy over a
corpus of sentence translations and selects a favorable member of the
family (EDPM) based on this comparison. Section~\ref{sec:hter1} compares
the correlation of EDPM with HTER over a corpus of document- and
sentence-level comparisons, and demonstrates that its correlation is
favorable to that of competitor measures BLEU and TER at both sentence
and document levels, regardless of source-language or genre.
Section~\ref{sec:hter2} uses the tuning components of the TERp tools
to explore the combination of these syntactic measures with other
TERp-based word-based measures. Finally, section~\ref{sec:conclusion}
concludes with some remarks on challenges and future work.

@@

\section{Experimental paradigm}
\label{sec:paradigm}
In this section, we describe the details of the implementation and
experimental variables explored in the experiments presented here.
